Kung Faux Pandas \\ \large Simplifying Privacy Protection

### 2018-06-03 paper/main.tex
Auto Update from local Sharelatex

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2018}

@@

There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.

@@

In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.  Thus, even institutions which share data face a steep institutional risk. This makes it virtually impossible to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.

@@

One obvious way around this pickle is to separate data and analysis in such a way that the analysis can be performed on data without the \emph{analyst} having access to the data.   This is fairly straight-forward to implement.   Essentially, the analyst, with only a description of the sensitive data, composes analytical code which is handed off to the data custodian.  The custodian then runs it and returns the results to the researcher.

@@

Kung Faux Pandas sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.

This faux-data can be prodded, poked, plotted, and posted for the world to see, enabling analysts to develop their code using whatever means they prefer.   When the analytical code is ready, it can then be sent to the data custodian to run on the real data.

@@

% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container

@@

%* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)
%* Individual states have adopted minimum group size reporting rules, with the minimum number of students ranging from 5 to 30 and a modal category of 10 (used by 39 states) https://nces.ed.gov/pubs2011/2011603.pdf
%* 62 https://nces.ed.gov/nationsreportcard/tdw/analysis/summary_rules_minimum.aspx
%* 30; describes techniques to determine size - https://nces.ed.gov/pubs2017/2017147.pdf

>>>>

% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage[final]{nips_2018}

@@

% two references don't seem to represent a large body of published literature. Change wording? Include more references?
There is a large body of published literature detailing methods for overcoming this difficulty via ``anonymizing'' and ``synthesising'' data \cite{patki_synthetic_2016, choi_generating_2017}, however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.

@@

 Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}. Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment. One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by the traditional research paper \cite{schwab_making_2000}. The previously mentioned authors propose that reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}. Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly. Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.

% clarify this section; how does HIPAA allow data to be shared? BAA or De-identification are main methods
In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.  Thus, even institutions which share data face a steep institutional risk. This makes it virtually impossible to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.

@@

% Logical step our work is taking. 
One obvious way around this pickle is to separate data and analysis in such a way that the analysis can be performed on data without the \emph{analyst} having access to the data.   This is fairly straight-forward to implement.   Essentially, the analyst, with only a description of the sensitive data, composes analytical code which is handed off to the data custodian.  The custodian then runs it and returns the results to the researcher.

@@

% What is our major contribution to the area of reproducibility in machine learning?
Kung Faux Pandas sidesteps this problem by generating \emph{faux-data} that is ``statistically similar'' to the real data but does not itself contain any sensitive data.

% this is a key unique feature of this work and should likely be repeated in conclusion. Perhaps also include in abstract
This faux-data can be prodded, poked, plotted, and posted for the world to see, enabling analysts to develop their code using whatever means they prefer.   When the analytical code is ready, it can then be sent to the data custodian to run on the real data.

@@

% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
% where to put this text? "Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."

@@

% Some information about minimum group size
%* Minimum group/result set size depends on several factors such as re-identification risk, number of attributes available (see picture at end)
%* Individual states have adopted minimum group size reporting rules, with the minimum number of students ranging from 5 to 30 and a modal category of 10 (used by 39 states) https://nces.ed.gov/pubs2011/2011603.pdf
%* 62 https://nces.ed.gov/nationsreportcard/tdw/analysis/summary_rules_minimum.aspx
%* 30; describes techniques to determine size - https://nces.ed.gov/pubs2017/2017147.pdf
